Models of VOR learning in MHC knockout mice

### 2013-01-29 Notes/VORmodel.tex
row refs

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\KO}{D$^\mathrm{b}$K$^\mathrm{b}$-/-}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
\newcommand{\lmax}{_{\text{max}}}
\newcommand{\lmin}{_{\text{min}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Models of VOR learning in MHC knockout mice}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

\begin{table}
 \begin{center}
  \begin{tabular}{|l|c|c|c|c|c|c|}
    \hline
    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
    Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $r\ttrain$ & $r\tpre$ \\
    \hline
    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 50  \\
    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 150 \\
    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.1 & 50 & 50  \\
    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.4 & 20 & 20  \\
    Two-state  & 2  & $q=0.4$  & $q=0.8$  & -0.1 & 5  & 5   \\
    Pooled     & 10 & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
                                          & -0.1 & 70 & 70 \\
    Pooled     & 10 & $q\in[0.1,0.4]$  & $q\in[0.2,0.8]$
                                          & -0.1 & 70 & 70 \\
    \hline
  \end{tabular}
 \end{center}
  \caption{Parameters used in simulations.} \label{tab:params}
\end{table}

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{cascade_short_learn.eps}}\label{fig:cascade_short_learn}
  \item\aligntop{\includegraphics[width=7cm]{cascade_short_learnS.eps}}\label{fig:cascade_short_learnS}
  \item\label{fig:cascade_short_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_short_eq_WT.eps}}\label{fig:cascade_short_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_short_eq_KO.eps}}\label{fig:cascade_short_eq_KO}
                  \end{myenumi}
  \item\label{fig:cascade_short_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_WT_nopre.eps}}\label{fig:cascade_short_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_WT_pre.eps}}\label{fig:cascade_short_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_KO_nopre.eps}}\label{fig:cascade_short_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_KO_pre.eps}}\label{fig:cascade_short_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for cascade model with short pre-training ($rt_\text{pre}=50$).
  Other parameters can be found in \autoref{tab:params}.
  (\ref{fig:cascade_short_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:cascade_short_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:cascade_short_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:cascade_short_eq_WT}) wild-type and (\ref{fig:cascade_short_eq_KO}) \KO\ mutant.
  (\ref{fig:cascade_short_pr}) Evolution of probability distributions for (\ref{fig:cascade_short_pr_WT_nopre}\ref{fig:cascade_short_pr_WT_pre}) wild-type and  (\ref{fig:cascade_short_pr_KO_nopre}\ref{fig:cascade_short_pr_KO_pre}) \KO\ mutant without (\ref{fig:cascade_short_pr_WT_nopre},\ref{fig:cascade_short_pr_KO_nopre}) and with (\ref{fig:cascade_short_pr_WT_pre},\ref{fig:cascade_short_pr_KO_pre}) pre-training. } \label{fig:cascade_short}
\end{figure}

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{cascade_long_learn.eps}}\label{fig:cascade_long_learn}
  \item\aligntop{\includegraphics[width=7cm]{cascade_long_learnS.eps}}\label{fig:cascade_long_learnS}
  \item\label{fig:cascade_long_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_long_eq_WT.eps}}\label{fig:cascade_long_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_long_eq_KO.eps}}\label{fig:cascade_long_eq_KO}
                  \end{myenumi}
  \item\label{fig:cascade_long_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_WT_nopre.eps}}\label{fig:cascade_long_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_WT_pre.eps}}\label{fig:cascade_long_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_KO_nopre.eps}}\label{fig:cascade_long_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_KO_pre.eps}}\label{fig:cascade_long_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for cascade model with long pre-training ($rt_\text{pre}=150$).
  Other parameters can be found in \autoref{tab:params}.
  (\ref{fig:cascade_long_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:cascade_long_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:cascade_long_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:cascade_long_eq_WT}) wild-type and (\ref{fig:cascade_long_eq_KO}) \KO\ mutant.
  (\ref{fig:cascade_long_pr}) Evolution of probability distributions for (\ref{fig:cascade_long_pr_WT_nopre}\ref{fig:cascade_long_pr_WT_pre}) wild-type and  (\ref{fig:cascade_long_pr_KO_nopre}\ref{fig:cascade_long_pr_KO_pre}) \KO\ mutant without (\ref{fig:cascade_long_pr_WT_nopre},\ref{fig:cascade_long_pr_KO_nopre}) and with (\ref{fig:cascade_long_pr_WT_pre},\ref{fig:cascade_long_pr_KO_pre}) pre-training. } \label{fig:cascade_long}
\end{figure}

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{multistate_weak_learn.eps}}\label{fig:multistate_weak_learn}
  \item\aligntop{\includegraphics[width=7cm]{multistate_weak_learnS.eps}}\label{fig:multistate_weak_learnS}
  \item\label{fig:multistate_weak_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_weak_eq_WT.eps}}\label{fig:multistate_weak_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_weak_eq_KO.eps}}\label{fig:multistate_weak_eq_KO}
                  \end{myenumi}
  \item\label{fig:multistate_weak_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_WT_nopre.eps}}\label{fig:multistate_weak_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_WT_pre.eps}}\label{fig:multistate_weak_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_KO_nopre.eps}}\label{fig:multistate_weak_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_KO_pre.eps}}\label{fig:multistate_weak_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for multistate model with weak training ($\Delta f=-0.1$).
  Other parameters can be found in \autoref{tab:params}.
  (\ref{fig:multistate_weak_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:multistate_weak_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:multistate_weak_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:multistate_weak_eq_WT}) wild-type and (\ref{fig:multistate_weak_eq_KO}) \KO\ mutant.
  (\ref{fig:multistate_weak_pr}) Evolution of probability distributions for (\ref{fig:multistate_weak_pr_WT_nopre}\ref{fig:multistate_weak_pr_WT_pre}) wild-type and  (\ref{fig:multistate_weak_pr_KO_nopre}\ref{fig:multistate_weak_pr_KO_pre}) \KO\ mutant without (\ref{fig:multistate_weak_pr_WT_nopre},\ref{fig:multistate_weak_pr_KO_nopre}) and with (\ref{fig:multistate_weak_pr_WT_pre},\ref{fig:multistate_weak_pr_KO_pre}) pre-training. } \label{fig:multistate_weak}
\end{figure}

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{multistate_strong_learn.eps}}\label{fig:multistate_strong_learn}
  \item\aligntop{\includegraphics[width=7cm]{multistate_strong_learnS.eps}}\label{fig:multistate_strong_learnS}
  \item\label{fig:multistate_strong_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_strong_eq_WT.eps}}\label{fig:multistate_strong_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_strong_eq_KO.eps}}\label{fig:multistate_strong_eq_KO}
                  \end{myenumi}
  \item\label{fig:multistate_strong_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_WT_nopre.eps}}\label{fig:multistate_strong_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_WT_pre.eps}}\label{fig:multistate_strong_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_KO_nopre.eps}}\label{fig:multistate_strong_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_KO_pre.eps}}\label{fig:multistate_strong_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for multistate model with strong training ($\Delta f=-0.4$).
  Other parameters can be found in \autoref{tab:params}.
  (\ref{fig:multistate_strong_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:multistate_strong_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:multistate_strong_eq}) Equilibrium distributions with/without gain-increase/decrease training for (\ref{fig:multistate_strong_eq_WT}) wild-type and (\ref{fig:multistate_strong_eq_KO}) \KO\ mutant.
  (\ref{fig:multistate_strong_pr}) Evolution of probability distributions for (\ref{fig:multistate_strong_pr_WT_nopre}\ref{fig:multistate_strong_pr_WT_pre}) wild-type and  (\ref{fig:multistate_strong_pr_KO_nopre}\ref{fig:multistate_strong_pr_KO_pre}) \KO\ mutant without (\ref{fig:multistate_strong_pr_WT_nopre},\ref{fig:multistate_strong_pr_KO_nopre}) and with (\ref{fig:multistate_strong_pr_WT_pre},\ref{fig:multistate_strong_pr_KO_pre}) pre-training. } \label{fig:multistate_strong}
\end{figure}

>>>>

% -*- TeX -*- -*- UK -*-
% ----------------------------------------------------------------
% arXiv Paper ************************************************
%
% Subhaneil Lahiri's template
%
% Before submitting:
%    Comment out hyperref
%    Comment out showkeys
%    Replace \input{mydefs.tex} with its contents
%       or include mydefs.tex in zip/tar file
%    Replace \input{newsymb.tex} with its contents
%       or include newsymb.tex in zip/tar file
%    Put this file, the .bbl file, any picture or
%       other additional files and natbib.sty
%       file in a zip/tar file
%
% **** -----------------------------------------------------------
\documentclass[12pt]{article}
%Preamble:
\usepackage{a4wide}
\input{sl_preamble.tex}
\input{sl_graphics_preamble.tex}
\graphicspath{{"Figures/"}}
%
\usepackage{array}
\newcounter{tablerow}
\newcommand{\tablerowautorefname}{row}
\newenvironment{tabularn}[1]{\setcounter{tablerow}{0}\begin{tabular}{#1>{\refstepcounter{tablerow}}l}}{\end{tabular}}
%\usepackage{etoolbox}
%\AtBeginEnvironment{tabular}{\setcounter{tablerow}{0}}
%
% >> Only for drafts! <<
\usepackage[notref,notcite]{showkeys}
% ----------------------------------------------------------------
%\numberwithin{equation}{section}
%\renewcommand{\baselinestretch}{1.5}
% ----------------------------------------------------------------
% New commands etc.
\input{sl_definitions.tex}
\input{sl_symbols.tex}
%matrices
\newcommand{\inv}{^{-1}}
\newcommand{\dg}{^\mathrm{dg}}
\newcommand{\trans}{^\mathrm{T}}
\newcommand{\I}{\mathbf{I}}
%vec of ones
\newcommand{\onev}{\mathbf{e}}
%mat of ones
\newcommand{\onem}{\mathbf{E}}
%Markov matrix
\newcommand{\MM}{\mathbf{Q}}
%equilibrium distribution
\newcommand{\pr}{\mathbf{p}}
\newcommand{\eq}{\pr^\infty}
%first passage times
\newcommand{\fpt}{\mathbf{T}}
%off-diag first passage times
\newcommand{\fptb}{\overline{\fpt}}
%fundamental matrix
\newcommand{\fund}{\mathbf{Z}}
%other symbols
\newcommand{\Pb}{\mathbf{P}}
\newcommand{\D}{\mathbf{D}}
\newcommand{\pib}{\boldsymbol{\pi}}
\newcommand{\Lb}{\boldsymbol{\Lambda}}
\newcommand{\w}{\mathbf{w}}
\newcommand{\W}{\mathbf{W}}
\newcommand{\frg}{\W^\mathrm{F}}
\newcommand{\M}{\mathbf{M}}
\newcommand{\F}{\boldsymbol{\Phi}}
\DeclareMathOperator{\SNR}{SNR}
\newcommand{\CS}{\mathcal{S}}
\newcommand{\CA}{\mathcal{A}}
\newcommand{\CB}{\mathcal{B}}
\newcommand{\comp}{^\mathrm{c}}
\newcommand{\pot}{^{\text{pot}}}
\newcommand{\dep}{^{\text{dep}}}
\newcommand{\potdep}{^{\text{pot/dep}}}
\newcommand{\norm}{_0}
\newcommand{\inc}{_{\text{inc}}}
\newcommand{\dec}{_{\text{dec}}}
\newcommand{\incdec}{_{\text{inc/dec}}}
\newcommand{\wt}{_{\text{WT}}}
\newcommand{\ko}{_{\text{D$^\mathrm{b}$K$^\mathrm{b}$-/-}}}
\newcommand{\KO}{D$^\mathrm{b}$K$^\mathrm{b}$-/-}
\newcommand{\tpre}{t_{\text{pre}}}
\newcommand{\ttrain}{t_{\text{train}}}
\newcommand{\lmax}{_{\text{max}}}
\newcommand{\lmin}{_{\text{min}}}
% ----------------------------------------------------------------
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Title info:
\title{Models of VOR learning in MHC knockout mice}
%
% Author List:
%
\author{Subhaneil Lahiri
%
}

@@

\begin{table}
 \begin{center}
  \begin{tabularn}{|l|c|c|c|c|c|c|}
%  \begin{tabular}{|l|c|c|c|c|c|c|>{\refstepcounter{tablerow}}l}
    \cline{1-7}
    % after \\: \hline or \cline{col1-col2} \cline{col3-col4} ...
    Model & \# states & pot,WT dep & \KO\ dep & $\Delta f$ & $r\ttrain$ & $r\tpre$ \\
    \cline{1-7}
    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 50  &\label{tr:cascade_short} \\
    Cascade    & 10 & $x=0.25$ & $x=0.33$ & -0.3 & 50 & 150 &\label{tr:cascade_long} \\
    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.1 & 50 & 50  &\label{tr:multistate_weak} \\
    Multistate & 10 & $q=0.6$  & $q=0.8$  & -0.4 & 20 & 20  & \label{tr:multistate_strong} \\
    Two-state  & 2  & $q=0.4$  & $q=0.8$  & -0.1 & 5  & 5   &\label{tr:binary} \\
    Pooled     & 10 & $q\in[0.3,0.4]$  & $q\in[0.6,0.8]$
                                          & -0.1 & 70 & 70 &\label{tr:pooled_plenty}\\
    Pooled     & 10 & $q\in[0.1,0.4]$  & $q\in[0.2,0.8]$
                                          & -0.1 & 70 & 70 &\label{tr:pooled_scarce}\\
    \cline{1-7}
  \end{tabularn}
 \end{center}
  \caption{Parameters used in simulations.} \label{tab:params}
\end{table}

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{cascade_short_learn.eps}}\label{fig:cascade_short_learn}
  \item\aligntop{\includegraphics[width=7cm]{cascade_short_learnS.eps}}\label{fig:cascade_short_learnS}
  \item\label{fig:cascade_short_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_short_eq_WT.eps}}\label{fig:cascade_short_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_short_eq_KO.eps}}\label{fig:cascade_short_eq_KO}
                  \end{myenumi}
  \item\label{fig:cascade_short_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_WT_nopre.eps}}\label{fig:cascade_short_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_WT_pre.eps}}\label{fig:cascade_short_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_KO_nopre.eps}}\label{fig:cascade_short_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_short_pr_KO_pre.eps}}\label{fig:cascade_short_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for cascade model with short pre-training ($rt_\text{pre}=50$).
  Other parameters can be found in \autoref{tr:cascade_short} of \autoref{tab:params}.
  (\ref{fig:cascade_short_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:cascade_short_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:cascade_short_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:cascade_short_eq_WT}) wild-type and (\ref{fig:cascade_short_eq_KO}) \KO\ mutant.
  (\ref{fig:cascade_short_pr}) Evolution of probability distributions for (\ref{fig:cascade_short_pr_WT_nopre}\ref{fig:cascade_short_pr_WT_pre}) wild-type and  (\ref{fig:cascade_short_pr_KO_nopre}\ref{fig:cascade_short_pr_KO_pre}) \KO\ mutant without (\ref{fig:cascade_short_pr_WT_nopre},\ref{fig:cascade_short_pr_KO_nopre}) and with (\ref{fig:cascade_short_pr_WT_pre},\ref{fig:cascade_short_pr_KO_pre}) pre-training. } \label{fig:cascade_short}
\end{figure}

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{cascade_long_learn.eps}}\label{fig:cascade_long_learn}
  \item\aligntop{\includegraphics[width=7cm]{cascade_long_learnS.eps}}\label{fig:cascade_long_learnS}
  \item\label{fig:cascade_long_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_long_eq_WT.eps}}\label{fig:cascade_long_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{cascade_long_eq_KO.eps}}\label{fig:cascade_long_eq_KO}
                  \end{myenumi}
  \item\label{fig:cascade_long_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_WT_nopre.eps}}\label{fig:cascade_long_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_WT_pre.eps}}\label{fig:cascade_long_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_KO_nopre.eps}}\label{fig:cascade_long_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{cascade_long_pr_KO_pre.eps}}\label{fig:cascade_long_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for cascade model with long pre-training ($rt_\text{pre}=150$).
  Other parameters can be found in \autoref{tr:cascade_long} of \autoref{tab:params}.
  (\ref{fig:cascade_long_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:cascade_long_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:cascade_long_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:cascade_long_eq_WT}) wild-type and (\ref{fig:cascade_long_eq_KO}) \KO\ mutant.
  (\ref{fig:cascade_long_pr}) Evolution of probability distributions for (\ref{fig:cascade_long_pr_WT_nopre}\ref{fig:cascade_long_pr_WT_pre}) wild-type and  (\ref{fig:cascade_long_pr_KO_nopre}\ref{fig:cascade_long_pr_KO_pre}) \KO\ mutant without (\ref{fig:cascade_long_pr_WT_nopre},\ref{fig:cascade_long_pr_KO_nopre}) and with (\ref{fig:cascade_long_pr_WT_pre},\ref{fig:cascade_long_pr_KO_pre}) pre-training. } \label{fig:cascade_long}
\end{figure}

@@

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{multistate_weak_learn.eps}}\label{fig:multistate_weak_learn}
  \item\aligntop{\includegraphics[width=7cm]{multistate_weak_learnS.eps}}\label{fig:multistate_weak_learnS}
  \item\label{fig:multistate_weak_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_weak_eq_WT.eps}}\label{fig:multistate_weak_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_weak_eq_KO.eps}}\label{fig:multistate_weak_eq_KO}
                  \end{myenumi}
  \item\label{fig:multistate_weak_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_WT_nopre.eps}}\label{fig:multistate_weak_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_WT_pre.eps}}\label{fig:multistate_weak_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_KO_nopre.eps}}\label{fig:multistate_weak_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_weak_pr_KO_pre.eps}}\label{fig:multistate_weak_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for multistate model with weak training ($\Delta f=-0.1$).
  Other parameters can be found in \autoref{tr:multistate_weak} of \autoref{tab:params}.
  (\ref{fig:multistate_weak_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:multistate_weak_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:multistate_weak_eq}) Equilibrium distributions without training or with gain-increase/decrease training for (\ref{fig:multistate_weak_eq_WT}) wild-type and (\ref{fig:multistate_weak_eq_KO}) \KO\ mutant.
  (\ref{fig:multistate_weak_pr}) Evolution of probability distributions for (\ref{fig:multistate_weak_pr_WT_nopre}\ref{fig:multistate_weak_pr_WT_pre}) wild-type and  (\ref{fig:multistate_weak_pr_KO_nopre}\ref{fig:multistate_weak_pr_KO_pre}) \KO\ mutant without (\ref{fig:multistate_weak_pr_WT_nopre},\ref{fig:multistate_weak_pr_KO_nopre}) and with (\ref{fig:multistate_weak_pr_WT_pre},\ref{fig:multistate_weak_pr_KO_pre}) pre-training. } \label{fig:multistate_weak}
\end{figure}

\begin{figure}
 \begin{center}
 \begin{myenuma}
  \item\aligntop{\includegraphics[width=7cm]{multistate_strong_learn.eps}}\label{fig:multistate_strong_learn}
  \item\aligntop{\includegraphics[width=7cm]{multistate_strong_learnS.eps}}\label{fig:multistate_strong_learnS}
  \item\label{fig:multistate_strong_eq}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_strong_eq_WT.eps}}\label{fig:multistate_strong_eq_WT}
                    \item\aligntop{\includegraphics[width=7cm]{multistate_strong_eq_KO.eps}}\label{fig:multistate_strong_eq_KO}
                  \end{myenumi}
  \item\label{fig:multistate_strong_pr}\begin{myenumi}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_WT_nopre.eps}}\label{fig:multistate_strong_pr_WT_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_WT_pre.eps}}\label{fig:multistate_strong_pr_WT_pre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_KO_nopre.eps}}\label{fig:multistate_strong_pr_KO_nopre}
                    \item\aligntop{\includegraphics[width=3cm]{multistate_strong_pr_KO_pre.eps}}\label{fig:multistate_strong_pr_KO_pre}
                  \end{myenumi}
 \end{myenuma}
 \end{center}
  \caption{Simulation results for multistate model with strong training ($\Delta f=-0.4$).
  Other parameters can be found in \autoref{tr:multistate_strong} of \autoref{tab:params}.
  (\ref{fig:multistate_strong_learn}) Learning curves for wild-type and \KO\ mutant with and without pre-training.
  (\ref{fig:multistate_strong_learnS}) Learning curves restricted to gain-increase training.
  (\ref{fig:multistate_strong_eq}) Equilibrium distributions with/without gain-increase/decrease training for (\ref{fig:multistate_strong_eq_WT}) wild-type and (\ref{fig:multistate_strong_eq_KO}) \KO\ mutant.
  (\ref{fig:multistate_strong_pr}) Evolution of probability distributions for (\ref{fig:multistate_strong_pr_WT_nopre}\ref{fig:multistate_strong_pr_WT_pre}) wild-type and  (\ref{fig:multistate_strong_pr_KO_nopre}\ref{fig:multistate_strong_pr_KO_pre}) \KO\ mutant without (\ref{fig:multistate_strong_pr_WT_nopre},\ref{fig:multistate_strong_pr_KO_nopre}) and with (\ref{fig:multistate_strong_pr_WT_pre},\ref{fig:multistate_strong_pr_KO_pre}) pre-training. } \label{fig:multistate_strong}
\end{figure}
